Summary of the things that I learned

### 2024-10-09 800-conclusion.tex
Expand "future work" section

Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar \C $ and $ \hat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar \C $, can be made to work on its Rezk completion $ \hat \C $.

>>>>

Also, since we saw that in univalent foundations, there are two nonequivalent definitions $ \bar \C $ and $ \hat \C $ for the category of retracts, it would be interesting to see how well Scott's and Taylor's proofs about $ \bar \C $, can be made to work on its Rezk completion $ \hat \C $. More generally, note that the Karoubi envelope is not specific to the material in this thesis.
For example, the Karoubi envelope of a `semi cartesian closed category' is a cartesian closed category, and the cartesian closed structure on $ \R $ in Scott's representation theorem can be viewed as a special case of this \autocite{hayashi-1985-semifunctors}. In another direction, the category of smooth manifolds can be constructed as the Karoubi envelope of the category $ \C $ of the open subsets of all Euclidean spaces, with smooth maps between them (see \autocite{Lawvere-Karoubi}, page 267). For such classical results about the Karoubi envelope, it would be interesting to study how they hold up in univalent foundations for the different choices $ \overline \C $ and $ \hat \C $ of `the Karoubi envelope'.
